Multi sky-view\\ 3D aerosol distribution recovery

### 2013-08-01 article.tex
Added Monte Carlo image
Bookmark

\bibitem{Bluestone2001}
a.~Bluestone, G.~Abdoulaev, C.~Schmitz, R.~Barbour, and A.~Hielscher,
  \enquote{{Three-dimensional optical tomography of hemodynamics in the human
  head},} Optics express \textbf{9}, 272--86 (2001).

@@

\bibitem{sun_composition}
Wikipedia, \enquote{{Sunlight --- Wikipedia\{,\} The Free Encyclopedia},}  (2012), \url{http://en.wikipedia.org/w/index.php?title=Sunlight\&oldid=502554571}.

\bibitem{Martonchik2009}
J.~V. Martonchik, R.~A. Kahn, and D.~J. Diner, \enquote{{Retrieval of aerosol
  properties over land using MISR observations},} in \enquote{Satellite Aerosol
  Remote Sensing over Land,} , A.~A. Kokhanovsky and G.~Leeuw, eds. (Springer
  Berlin Heidelberg, 2009), pp. 267--293.

@@

Optical lightfield and integral imaging~\cite{Stern2006,kim,Ng1948}
sample the optical radiance distribution in location and
direction. These are mainly used in small-scale setups. This paper
deals with a far larger scale, to estimate scatterer 3D spatial
distribution in the sky.  The atmosphere allows light to pass through
in multiple locations and directions. Light is affected by this
medium. Therefore, in this paper we lay out a principle to recover
this 3D distribution using measured and modeled light-fields
(Fig.~\ref{fig:groundgrid}).
\begin{figure*}[t!]
  \begin{center}
    \yoavcomment{\includegraphics[width=\linewidth]{images/groundtomog24.pdf}}
  \end{center}
  \caption{\small Lightfield imaging through a volumetric distribution
    in the atmosphere, using ground-based cameras.}
  \label{fig:groundgrid}
\end{figure*}
3D recovery of this medium has direct implications to various
scientific communities that either rely on remotely-sensed imagery,
study the atmosphere, or overcome the medium to see beyond. These
include meteorology, atmospheric sciences, volcanology, and
climatology.  Aerosol retrieval is important for understanding climate
evolution~\cite{Dayan2008,kalashnikova} and monitoring air
quality. Mapping aerosol density is significant to aviation safety,
which needs real time assessment of conditions and visibility around
flight paths.

@@

We rely on sky imaging from multiple directions and locations. Such
projection is similar to tomography in other scientific
domains~\cite{Bluestone2001}. However, the situation here is
distinct. Most tomography setups have a controlled and/or
multidirectional radiation source~\cite{Bluestone2001,messer}. In
contrast, our source is the uncontrolled, unidirectional
Sun. Moreover, typical tomography relies on a linear
model~\cite{gregson}: the pixel value is a linear combination of
components along a line of sight (LOS), or a multiplicative
combination (linearized by a logarithm). Linear tomography can detect
gases~\cite{Cosofret2009}, which absorb UV or IR radiation. However,
aerosol attenuation of visible light is typically dominated by {\em
  scattering}, rather than absorption. Since the radiation source is
single and fixed in space and time, we cannot rely on direct
illumination for tomographic recovery of attenuation
fields~\cite{Aviles2011}. We may only use sunlight scattered into the
LOS. The model is {\em nonlinear, yet tractable}. We model passive
optical tomographic imaging of 3D atmospheric scatterer distributions
in cloudless conditions. Then, we solve this tomography problem, to
recover the distribution. Recovery is formulated as an optimization
that minimizes a cost function. We derive the gradient of this cost
function, to enable efficient optimization.

@@

The atmosphere is discretized into a grid of $N_{\rm voxels}$ volume
elements (voxels), indexed by $k$, $m$ or $q$. In a
\emph{single-scattering} model, any SR changes direction only once on
the way to a camera. This model is valid in atmospheres that are not
very dense: inside fog and clouds this model does not apply. In this
model, RT has three steps (\cref{fig:groundgrid}):
({\tt i}) Attenuation of a SR propagating from the top of the
atmosphere (TOA) to voxel $k$. ~({\tt ii}) Light scattering at voxel
$k$, towards a camera. ~({\tt iii}) Light attenuation on the LOS from
voxel $k$ to the camera.~~ Steps~{\tt i},{\tt iii} involve the optical
depth along the light path to and from voxel $k$, as analyzed in
\cref{sec:optical-depth}.  Step~{\tt ii} involves the scattering
coefficient at voxel $k$, described in \cref{sec:scattering}.

@@

The MC simulations rely on the same grid as
Sec.~\ref{sec:single-scatt-model}. We use backward MC: from a detector
pixel, photons are `launched' via the camera lens; then the photons
are traced back through the atmosphere. Photons that happen to be
back-traced to the Sun are counted, per pixel. In this model, RT takes
the following steps, per launched photon (\cref{fig:mcgrid}):

\noindent ({\tt v}) The photon is scattered to a new direction, determined by
inverse transform sampling, according to the phase function of the
particle: \cref{eq:aerosol_scatter} or~\cref{eq:rayleighP}. This
yields a new {\em ray}, denoted ${\cal R}_{i+1}$, emanating from ${\bf
  X}_{i}$. The next iteration of propagation (denoted {\tt ii} above)
proceeds.

\noindent Local Estimation~\cite{marshak20053d} is used for calculating the
amount of light back-traced to the sun at each scattering.

@@

The second function, $f_2$, expresses a clustered nature of aerosol
``clouds''. We define blobs in the form of 3D ellipsoids. There may be
multiple ellipsoids suspended.  Then
\begin{equation}
  f_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then
\begin{equation}
  \label{eq:ntrue}
  {\bm n}^{\rm true}={\bm f}_1\odot {\bm f}_2  .
  \hspace{-0.05cm}
\end{equation}
As an example, we created a {\em Haze Blobs} scene using two ellipsoid
blobs (\cref{fig:results}a): the first is centered at altitude
\SI{3.3}{\km}, and has horizontal width of \SI{32}{\km} and vertical
thickness of \SI{2.8}{\km}. The second ellipsoid is centered at
altitude \SI{6.6}{\km}, and has lateral width of \SI{24}{\km} and
vertical thickness of \SI{2.1}{\km}. Note that the horizontal widths
are much larger than the vertical ones. This is consistent with scales
of atmospheric aerosol distributions.
\\

@@

@@

We applied the reconstruction algorithm \cref{sec:inverse-problem} to
the images simulated in \cref{sec:simul}. We used the L-BFGS-B
algorithm~\cite{BFGS} on a computer cluster. Each core was dedicated
to rendering a modeled image. The algorithm was initialized by ${\bm
  n}=0$. Satisfactory convergence occurred in several thousand
iterations, taking a couple of hours to complete in total.

An iso-surface visualization of the original {\em Haze Blobs}
distribution is shown in \cref{fig:results}a. \cref{fig:results}c show
the reconstructed scene based on images simulated by the Single
Scattering model. \cref{fig:results}e visualizes the reconstructed
scene based on images simulated by the MC model. The distributions
appear consistent, though there are errors that stem from the random
noise in the images. To quantify the results, we use a relative error
measure based on the $\ell_1$ norm
\begin{equation}
  \label{eq:ndiff}
  \epsilon=\frac{\| \hat{\bm n}  - {\bm n}^{\rm true} \|_1}
  {\| {\bm n}^{\rm true} \|_1} ,
\end{equation}
It is equivalent to the aerosol mass that is over and under-estimated
in all voxels, relative to the total aerosol mass in the scene.  In
the {\em Haze Blobs} case, $\epsilon=0.143$ and $\epsilon=0.646$ for
the reconstructions based on the Single-Scattering images and MC
images respectively. We used the distribution reconstructed based on
the MC images to create images using the Single-Scattering
model. \cref{fig:simulation-results1}c shows a cross of such an image
compared to the original MC image.

We created a {\em Haze Front} scene. \cref{fig:results}b shows an
iso-surface visualization of this distribution.
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/results}}
  \caption{\small [a] and [b] Simulated 3D aerosol distribution
    composed of a {\em Haze Front} and {\em Haze Front}
    respectively. [c] and [d] Reconstruction of the same scenes when
    using Single-Scattering simulated images as input.  [e] and [f]
    Reconstruction of the scenes when using MC simulated images as
    input.  Color represents aerosol density. The density units are
    $10^{6}~{\rm particles}/{\rm m}^3.$}
  \label{fig:results}
\end{figure}
Here an ellipsoid degenerated to an elliptic cylinder that partly
enters the analyzed volume. It is centered at altitude \SI{5}{\km},
has vertical thickness of \SI{4}{\km} and length of \SI{32}{\km} (only
part of which enters the volume). The haze front stretches across the
width of the volume.  \cref{fig:results}d and \cref{fig:results}f
visualizes the recovered 3D distribution of this scene. For the {\em
  Haze Front}, $\epsilon=0.199$ and $\epsilon=0.654$ for the
reconstructions based on the Single-Scattering images and MC images
respectively.

@@

>>>>

\bibitem{Bluestone2001}
A.~Bluestone, G.~Abdoulaev, C.~Schmitz, R.~Barbour, and A.~Hielscher,
  \enquote{{Three-dimensional optical tomography of hemodynamics in the human
  head},} Optics express \textbf{9}, 272--86 (2001).

\bibitem{Boas2001}
D.~A. Boas, D.~H. Brooks, E.~L. Miller, C.~A. DiMarzio, M.~Kilmer, R.~J.
  Gaudette, and Q.~Zhang, \enquote{{Imaging the body with diffuse optical
  tomography},} Sig.Proc. Magazine \textbf{18}, 57--75 (2001).

@@

\bibitem{sun_composition}
Wikipedia, \enquote{{Sunlight --- {W}ikipedia{,} The Free Encyclopedia},}  (2012), \url{http://en.wikipedia.org/w/index.php?title=Sunlight\&oldid=502554571}.

\bibitem{Martonchik2009}
J.~V. Martonchik, R.~A. Kahn, and D.~J. Diner, \enquote{{Retrieval of aerosol
  properties over land using MISR observations},} in \emph{{Satellite Aerosol
  Remote Sensing over Land,}} , A.~A. Kokhanovsky and G.~Leeuw, eds. (Springer
  Berlin Heidelberg, 2009), pp. 267--293.

@@

Optical lightfield and integral imaging~\cite{Stern2006,kim,Ng1948}
sample the optical radiance distribution in location and
direction. These are mainly used in small-scale setups. This paper
deals with a far larger scale, to estimate scatterer 3D spatial
distribution in the sky.  The atmosphere allows light to pass through
in multiple locations and directions. Light is affected by this
medium. Therefore, in this paper we lay out a principle to recover
this 3D distribution using measured and modeled light-fields
(Fig.~\ref{fig:groundgrid}).
3D recovery of this medium has direct implications to various
scientific communities that either rely on remotely-sensed imagery,
study the atmosphere, or overcome the medium to see beyond. These
include meteorology, atmospheric sciences, volcanology, and
climatology.  Aerosol retrieval is important for understanding climate
evolution~\cite{Dayan2008,kalashnikova} and monitoring air
quality. Mapping aerosol density is significant to aviation safety,
which needs real time assessment of conditions and visibility around
flight paths.

@@

We rely on sky imaging from multiple directions and locations. Such
projection is similar to tomography in other scientific
domains~\cite{Bluestone2001}. However, the situation here is
distinct. Most tomography setups have a controlled and/or
multidirectional radiation source~\cite{Boas2001,messer}. In
contrast, our source is the uncontrolled, unidirectional
Sun. Moreover, typical tomography relies on a linear
model~\cite{gregson}: the pixel value is a linear combination of
components along a line of sight (LOS), or a multiplicative
combination (linearized by a logarithm). Linear tomography can detect
gases~\cite{Cosofret2009}, which absorb UV or IR radiation. However,
aerosol attenuation of visible light is typically dominated by {\em
  scattering}, rather than absorption. Since the radiation source is
single and fixed in space and time, we cannot rely on direct
illumination for tomographic recovery of attenuation
fields~\cite{Aviles2011}. We may only use sunlight scattered into the
LOS. The model is {\em nonlinear, yet tractable}. We model passive
optical tomographic imaging of 3D atmospheric scatterer distributions
in cloudless conditions. Then, we solve this tomography problem, to
recover the distribution. Recovery is formulated as an optimization
that minimizes a cost function. We derive the gradient of this cost
function, to enable efficient optimization.
\begin{figure*}[t!]
  \begin{center}
    \yoavcomment{\includegraphics[width=\linewidth]{images/groundtomog24.pdf}}
  \end{center}
  \caption{\small Lightfield imaging through a volumetric distribution
    in the atmosphere, using ground-based cameras.}
  \label{fig:groundgrid}
\end{figure*}

@@

The atmosphere is discretized into a grid of $N_{\rm voxels}$ volume
elements (voxels), indexed by $k$, $m$ or $q$. \cref{fig:distributions}.
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/distributions}}
  \caption{\small [a] and [b] Simulated 3D aerosol distribution
    composed of a {\em Haze Front} and {\em Haze Front}
    respectively. The density units are $10^{6}~{\rm particles}/{\rm
      m}^3.$}
  \label{fig:distributions}
\end{figure}
In a \emph{single-scattering} model, any SR changes direction only
once on the way to a camera. This model is valid in atmospheres that
are not very dense: inside fog and clouds this model does not
apply. In this model, RT has three steps (\cref{fig:groundgrid}):
({\tt i}) Attenuation of a SR propagating from the top of the
atmosphere (TOA) to voxel $k$. ~({\tt ii}) Light scattering at voxel
$k$, towards a camera. ~({\tt iii}) Light attenuation on the LOS from
voxel $k$ to the camera.~~ Steps~{\tt i},{\tt iii} involve the optical
depth along the light path to and from voxel $k$, as analyzed in
\cref{sec:optical-depth}.  Step~{\tt ii} involves the scattering
coefficient at voxel $k$, described in \cref{sec:scattering}.

@@

@@

The second function, $f_2$, expresses a clustered nature of aerosol
``clouds''. We define blobs in the form of 3D ellipsoids. There may be
multiple ellipsoids suspended.  Then
\begin{equation}
  f_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then
\begin{equation}
  \label{eq:ntrue}
  {\bm n}^{\rm true}={\bm f}_1\odot {\bm f}_2  .
  \hspace{-0.05cm}
\end{equation}
As an example, we created a {\em Haze Blobs} scene using two ellipsoid
blobs (\cref{fig:distributions}a): the first is centered at altitude
\SI{3.3}{\km}, and has horizontal width of \SI{32}{\km} and vertical
thickness of \SI{2.8}{\km}. The second ellipsoid is centered at
altitude \SI{6.6}{\km}, and has lateral width of \SI{24}{\km} and
vertical thickness of \SI{2.1}{\km}. Note that the horizontal widths
are much larger than the vertical ones. This is consistent with scales
of atmospheric aerosol distributions.
\\

@@

The MC simulations rely on the same grid as
Sec.~\ref{sec:single-scatt-model}. We use backward MC: from a detector
pixel, photons are `launched' via the camera lens; then the photons
are traced back through the atmosphere. Photons that happen to be
back-traced to the Sun are counted, per pixel. In this model, RT takes
the following steps, per launched photon (\cref{fig:mcgrid}):
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=0.5\linewidth]{images/mcgrid.pdf}}
  \caption{\small Monte Carlo simulation of multiple-scattering
    radiative transfer.}
  \label{fig:mcgrid}
\end{figure}

\noindent ({\tt v}) The photon is scattered to a new direction,
determined by inverse transform sampling, according to the phase
function of the particle: \cref{eq:aerosol_scatter}
or~\cref{eq:rayleighP}. This yields a new {\em ray}, denoted ${\cal
  R}_{i+1}$, emanating from ${\bf X}_{i}$. Local
Estimation~\cite{marshak20053d} is used for calculating the amount of
light back-traced to the sun at each scattering. The next iteration of
propagation (denoted {\tt ii} above) proceeds.

@@

\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/results}}
  \caption{\small [a] and [b] Reconstruction of the scenes shown in
    \cref{fig:distributions} when using Single-Scattering simulated
    images as input.  [c] and [d] Reconstruction of the same scenes
    when using MC simulated images as input.  Color represents aerosol
    density. The density units are $10^{6}~{\rm particles}/{\rm
      m}^3.$}
  \label{fig:results}
\end{figure}
We applied the reconstruction algorithm \cref{sec:inverse-problem} to
the images simulated in \cref{sec:simul}. We used the L-BFGS-B
algorithm~\cite{BFGS} on a computer cluster. Each core was dedicated
to rendering a modeled image. The algorithm was initialized by ${\bm
  n}=0$. Satisfactory convergence occurred in several thousand
iterations, taking a couple of hours to complete in total.

An iso-surface visualization of the original {\em Haze Blobs}
distribution is shown in
\cref{fig:distributions}a. \cref{fig:results}a show the reconstructed
scene based on images simulated by the Single Scattering
model. \cref{fig:results}c visualizes the reconstructed scene based on
images simulated by the MC model. The distributions appear consistent,
though there are errors that stem from the random noise in the
images. To quantify the results, we use a relative error measure based
on the $\ell_1$ norm: $\epsilon=\sfrac{\| \hat{\bm n} - {\bm n}^{\rm
    true} \|_1} {\| {\bm n}^{\rm true} \|_1}$.  It is equivalent to
the aerosol mass that is over and under-estimated in all voxels,
relative to the total aerosol mass in the scene.  In the {\em Haze
  Blobs} case, $\epsilon=0.14$ and $\epsilon=0.65$ for the
reconstructions based on the Single-Scattering images and MC images
respectively. We used the distribution reconstructed based on the MC
images to create images using the Single-Scattering
model. \cref{fig:simulation-results1}c shows a cross of such an image
compared to the original MC image.

We created a {\em Haze Front} scene. \cref{fig:distributions}b shows
an iso-surface visualization of this distribution.
Here an ellipsoid degenerated to an elliptic cylinder that partly
enters the analyzed volume. It is centered at altitude \SI{5}{\km},
has vertical thickness of \SI{4}{\km} and length of \SI{32}{\km} (only
part of which enters the volume). The haze front stretches across the
width of the volume.  \cref{fig:results}b and \cref{fig:results}d
visualizes the recovered 3D distribution of this scene. For the {\em
  Haze Front}, $\epsilon=0.20$ and $\epsilon=0.65$ for the
reconstructions based on the Single-Scattering images and MC images
respectively.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%% Acknowledgments %%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Acknowledgments}
\label{sec:acknowledgments}

We thank Anthony~B. Davis and David~J. Diner for useful
discussions. Yoav Schechner is a Landau Fellow - supported by the Taub
Foundation. This work was conducted in the Ollendorff Minerva
Center. Minerva is funded through the BMBF.
